\textmd{\hmwkClass:\ \hmwkTitle}\\ \normalsize{\hmwkClassInstructor}\\ \small{Due\ on\ \hmwkDueDate}

### 2017-05-07 paper/main.tex
formatting

>>>>

Our engine updates each object every timestep and re-renders them on the screen:
\begin{verbatim}
(define (run-engine world steps)
  (reset-graphics)
  (if (> steps 0)
    (begin 
      (for-each 
        (lambda (thing)
            (newline)
            (display (cons (get-name thing) (get-position thing)))  ; for debugging
            (render thing))
        (get-world-all-things world))
      (update-world world)
    (run-engine world (- steps 1)))))
\end{verbatim}

where the \texttt{render} procedure takes in a \texttt{thing}, checks what type of thing it is, and renders the object appropriately.
